---
title: "My Munro Map"
author: "Rona Stewart"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

The purpose of this R Markdown file is to create a web page with an interactive map using the Leaflet library in R.  Specifically, this site will depict all of the Munros in Scotland, their height, region, and ranking (in height and prominence terms).  

### What is a Munro?
A Munro is a distinct Scottish peak of 3000ft (914.4m) and over, of "sufficient separation" from neighbouring peaks. The list was originally drawn up by Sir H.T. Munro in the Scottish Mountaineering Club Journal in 1891 was unfinished at the time of his death. Munro did not write down a precise definition of what he meant by "sufficient separation", though the character of a mountain did enter into it. Through regular use these hills have become known as the Munros. The current list contains 282 peaks.


### What does the map do?
The map shows the location of the top of each Munro, colour coded by whether the author has climbed the hill or not.  When the tag is selected, it provides the height, prominence and relative ranking amongst the Munros for both. 

### Generating the map
```{r MunroMap}
# First read the data in to R
hills <- read.csv("C:\\Users\\rona_\\Documents\\Data_Science\\Module_9\\DoBIHdata.csv")

# Then set up the Leaflet page and other required packages
library(leaflet); library(dplyr); library(tidyr)

# Add group colour as a factor variable to produce different coloured icons
hills <- hills %>%
  mutate(Group = case_when(
    Climbed == "Yes" ~ "darkgreen",
    Climbed == "No" ~ "red"),
    group_color = as.factor(Group))

# Set icons for climbed (green triangle) and not yet climbed (red triangle)
my_icon <- iconList(
                triangle_green <- makeIcon(iconUrl = "https://www.freeiconspng.com/uploads/green-normal-triangle-png-8.png",
                             iconWidth = 10, iconHeight = 10),
               triangle_red <- makeIcon(iconUrl = "https://www.freeiconspng.com/uploads/red-triangle-png-20.png",
                           iconWidth = 10, iconHeight = 10)
)

# Set pop-up text
hills <- mutate(hills, popup = paste(Name, 
                                paste("Height (m): ", Metres, sep=""),
                                paste("Height (ft): ", Feet, sep=""),
                                paste("Rank (height): ", height_rank, sep=""),
                                paste("Prominence(m): ", prominence_m, sep=""),
                                paste("Prominence(ft): ", prominence_ft, sep=""),
                                paste("Rank (Prominence): ", prominence_rank, sep = ""),
                                sep = "<br>"
                                )
                )

#Create map with markers, popups and legend
hills<- hills %>%
        leaflet() %>%
        addTiles() %>%
        addMarkers(lat = hills$Latitude, lng = hills$Longitude,
                   clusterOptions = markerClusterOptions(),
                   icon = ~ my_icon[as.numeric(group_color)],
                   popup = hills$popup) %>%
        addLegend(labels = c("Climbed", "Not yet climbed"), 
                  colors = c("darkgreen", "red"))

# Launch the map
hills

```

## Appendix 1: Data sources

Database of British and Irish hills
https://www.hills-database.co.uk/downloads.html

Scottish Mountaineering Club
https://www.smc.org.uk/

WalkHighlands
https://www.walkhighlands.co.uk/

Wikipedia
https://en.wikipedia.org/wiki/List_of_Munro_mountains